\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Eric Liang}} & Email : \href{mailto:ericzhiliang@gmail.com}{ericzhiliang@gmail.com}\\
  1-646-525-9401 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {NYU Tandon School of Engineering}{Brooklyn, NY}
      {Bachelor of Science in Computer Science;  GPA: 3.26}{2012 -- 2016}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Raytheon CODEX}{Annapolis Junction, MD}
      {Senior Cyber Engineer I}{Jan 2017 - Present}
      \resumeItemListStart
      \resumeItem{Structured Fuzzing W/ Coverage} {
        Structured fuzzing with coverage utilizing protobuf and libfuzzer to
        find memory corruption bugs.
        Fuzzing harnesses were created to recreate realistic behavior in various
        remote attack surfaces. 
        Auditing was done in tandem with harness creation to statically
        find bugs, understand program design, and model various program states. 
      }
      \resumeItem{Grammar Based Fuzzing} {
        Developed and researched fuzzers that generated syntatically and
        semantically valid grammar to explore complex program states in target
        that takes a programming language as input. Modified popular grammar
        based fuzzer with compiler phases to have type aware grammar generation,
        and type aware arguments for procedure calls.
      }
      \resumeItem{Code Auditing} { 
        Audited through modern C++ to look for potential bugs in
        target application with complex program states. Research was done to
        understand various APIs that can change said program states and understand various
        esoteric metalanguages in the codebase.
      }
      \resumeItem{N-Day Analysis} {
        Conducted research and created reports for multiple vulnerabilities.
        Analyzed usability of vulnerabilities for necessary context required for
        usage.
      }
      \resumeItemListEnd

    \resumeSubheading
      {Raytheon CODEX}{Annapolis Junction, MD}
      {Vulnerability Researcher Intern}{May 2015 - Aug 2015}
      \resumeItemListStart
        \resumeItem{Browser N-Day Research}{
          Developed and demonstrated a patched remote code execution utilizing a
          use-after-free bug in Internet Explorer 9's Document Object Model.
          Development required grooming of the Window's Low Fragmentation Heap,
          a heap spray (32-bit address space at the time), and
          return orientated programming to pivot to shellcode execution.
        }
        \resumeItem{Coverage Guided Feedback} {
          Created an intel pintool for coveraged guided feedback on a target
          application. Work was done to record all basic blocks reached by
          user input and aggregate coverage results.
        }
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%#--------TECHNICAL SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Python, Javascript, C++14, C, Bash}
      \hfill
    }
    \item{
      \textbf{Architectures}{: x86, x86-64, ARM, AArch64}
      \hfill
    }
    \item{
      \textbf{Tools}{: IDA Pro, libfuzzer, AFL, protobuf-mutator, gdb,
      adb, frida, git, docker}
      \hfill
    }
    \item{
      \textbf{Skills}{: Reverse Enginnering, Code Auditing, Shellcoding, Remote
      Code Execution, Sandbox Escape, IPC, Return Oriented Programming, Heapspray, 
      JIT, Heap Grooms, Exploit Development }
      \hfill
    }
    \item {
      \textbf{Systems}{: Linux, Android, Windows, Mac}
      \hfill
    }
  \resumeSubHeadingListEnd

\section{Miscellaneous}
  \resumeSubHeadingListStart
  \item{
      {2018 DEFCON CTF Finalist with Spaceballs(NasaRejects)}
    \hfill
  }
  \item{
      {CTF hobbyist}
    \hfill
  }
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
